Awareness and Experience of Developers to\\ Outdated and License-violating Code on Stack Overflow:\\ The Online Survey

### 2017-09-15 cloverflow_technical_report/cloverflow_survey_rn.tex
Technical report revision#1.

Asking and answering questions on Stack Overflow involves including source code
snippets, either in a question or an answer or both. While many answers contain
snippets that are written from scratch, there are several answers containing
code snippets copied from other sources. The copied snippets on Stack Overflow
is a snapshot of the code at the time of copying. They are less frequently
updated than in normal software projects and might not be up-to-date with their
originals, which are further modified due to bug fixing or feature improvements.
In addition, Some snippets are copied from software systems with stricter
license than Stack Overflow's Attribution-ShareAlike 3.0 Unported (CC BY-SA
3.0). Prior to this study, we performed a quantitative empirical study using
code clone detection tools to locate cloned code snippets in accepted answers.
We found that many snippets were copied from open source projects. Some cloned
snippets are outdated (or obsolete) and some possibly violate the original software license.
These snippets are potentially harmful to reuse. To accompany the findings and
gain insights into the cause of the problems, we resort to a qualitative study
using an online survey of Stack Overflow developers who 1) regularly answer
programming questions with code snippets and 2) reuse code snippets from Stack
Overflow. \textbf{The study aims to understand the developers' awareness and
	experience to the issues of outdated and license-violating code on Stack
	Overflow.}

@@

\section{Research Questions}
In this study, we would like to answer six research questions. The first three questions will be
answered by the Stack Overflow answerer survey, while the other three questions will be answered by the
Stack Overflow visitor survey.

@@

\section{Research Methodology}
The study is conducted using online surveys. We designed the surveys using
Google Forms by following the principles of survey research
by~\cite{Pfleeger2001} and~\cite{Kitchenham2002}. We created two versions of the
survey: \textbf{the answerer survey}, and, \textbf{the visitor survey}. Both
surveys are completely anonymous and the participants could decide to leave at
any time. They do not collect any sensitive personal information from the
participants and are approved for an ethical waiver by the designated ethics
officer in the Computer Science Department at University College London (UCL). 
The complete version of the surveys can be found in 
Appendix~\ref{appendixA}.

\subsection{The Answerer Survey}
The Stack Overflow answerer survey contains 11 questions: 7 Likert's scale
questions, 3 yes/no questions, and one open-ended question for additional
comments. The first two questions are mandatory while the other 9 questions will
be shown to the participants based on their previous answers. The survey
collects information of the participant's software development experience, the
experience of answering Stack Overflow questions, sources of the Stack Overflow
snippets, awareness of outdated code in their answers, concerns regarding
license when they copy code snippets to Stack Overflow, and additional feedbacks.

@@

We selected the participants for our answerer survey based on their Stack
Overflow reputations. On Stack Overflow, a user's reputation reflects how much
the community trusts the user. A user earns reputation when he or she receives
up votes for good questions and useful answers. Accepted answers receive more
reputation score than questions and regular answers\footnote{Stack Overflow
	Reputation:~\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
Overflow reputation is an indicator of user's skills and their involvement in
asking and answering questions on the site.

The participants were invited to take the survey via email addresses publicly
available on their Stack Overflow and GitHub profiles. We selected the answerers
based on their all-time reputation ranking\footnote{Stack Overflow Users (data as of
	25 July 2017):~\url{https://stackoverflow.com/users?tab=Reputation&filter=all}}
and separated them into two groups (see Table~\ref{tab:answerers}) so that we
can compare the results or observe similar patterns between them. The first
group had reputation from 963,731 (the highest) to 7,674, and the second group
had reputation from 7,636 to 6,999 which we sent out 300 and 307 emails
(excluding undelivered ones) respectively. The survey was open for participation
for a month, from 25 July 2017 to 25 August 2017, before we collected and
analysed the responses.ponses.

\subsection{The Visitor Survey}

The Stack Overflow visitor survey consists of 16 questions: 9 Likert's scale
questions, 3 yes/no questions, 2 multiple-choice questions, and 2 open-ended
questions. The first four questions were mandatory while the other 12 questions
were shown to the participants based on their previous answers. The survey collects
information of the participant's software development experience, the importance of
Stack Overflow, reasons for reusing Stack Overflow snippets, problems from
Stack Overflow snippets, licensing of code on Stack Overflow, and additional
feedbacks.

\begin{table}
	\centering
	\caption{The Stack Overflow visitors taken the survey}
	\label{tab:visitors}
	\begin{tabular}{lr}
		\toprule
		Invitation channels & Answers \\
		\midrule
		Social media (Facebook posts) & 47 \\
		Blognone.com & 32 \\
		University of Molise & 6 \\
		comp.lang.java.programmer & 3 \\
		Software Engineering Facebook page & 1 \\
		\midrule
		Total & 89 \\
		\bottomrule
	\end{tabular}
\end{table}

The participants for this survey were invited to take the survey via five
channels. The first channel is via the first author's Facebook post where the
first author invited friends who are software developers and have experience of
copying code snippets from Stack Overflow to take the survey. The second channel
is a popular Thai technology news and media community called blognone.com which
attracts a high number of software developers. The first author posted an
invitation to the visitor survey in a discussion forum. The third channel
collects answers from the University of Molise which is the third author's
workplace. The last two channels are from a comp.lang.java.programmer Google
groups and Software Engineering Facebook page. The survey was open for
participation for a month, from 25 July 2017 to 25 August 2017, before we
collected and analysed the responses. The number of participants taken the
survey is shown in Table~\ref{tab:visitors}.

\section{Results and Discussions}

\subsection{Answerer Responses}
We received 117 answers (39\% response rate) from the first group and 85 answers
(28\% response rate) from the second group of Stack Overflow answerers. The response
rate from both groups was high considered other online survey in software
engineering that received approximately 14--20\%~\FIXME{double-check the
	citation again for the magic numbers.}~\citep{Punter2003}.

\subsubsection*{General Information}
%General information of the answerers' experience and frequency of answering 
%questions on Stack Overflow with code snippets as discussed below.

@@

>>>>

Asking and answering questions on Stack Overflow involves including source code
snippets, either in a question or an answer or both. While many answers contain
snippets that are written from scratch, there are several answers containing
code snippets copied from other sources. The copied snippets on Stack Overflow
is a snapshot of the code at the time of copying. They are less frequently
updated than in normal software projects and might not be up-to-date with their
originals, which are further modified due to bug fixing or feature improvements.
In addition, Some snippets are copied from software systems with stricter
license than Stack Overflow's Attribution-ShareAlike 3.0 Unported (CC BY-SA
3.0). Prior to this study, we performed a quantitative empirical study using
code clone detection tools to locate cloned code snippets in accepted answers.
We found that many snippets were copied from open source projects. Some cloned
snippets are outdated (or obsolete) and some possibly violate the original software license.
These snippets are potentially harmful to reuse. To accompany the findings and
gain insights into the cause of the problems, we resort to a qualitative study
using an online survey of Stack Overflow developers who 1) regularly answer
programming questions with code snippets and 2) reuse code snippets from Stack
Overflow. \textbf{The study aims to understand the developers' awareness and
	experience to outdated code and code licensing on Stack
	Overflow.}

@@

\section{Research Methodology}
We followed the principles of survey research by~\cite{Pfleeger2001}
and~\cite{Kitchenham2002} by setting specific and measurable objective, 
designing and scheduling the survey, selecting participants, analysing the data, and reporting the results.
We now discuss each of them in detail.

\subsection{Survey Objective}
The main objective of the survey is to understand the developers' awareness and
experience to outdated code and code licensing on Stack Overflow. It can break
down into the following six research questions.

@@

The first three questions will be answered by
the Stack Overflow answerer survey, while the other three questions will be
answered by the Stack Overflow visitor survey.

\subsection{Survey Design and Schedule}
The study is conducted using unsupervised online surveys. We designed the surveys using
Google Forms. We created two versions of the
survey: \textbf{the answerer survey}, and, \textbf{the visitor survey}. Both
surveys are completely anonymous and the participants could decide to leave at
any time. They do not collect any sensitive personal information from the
participants and are approved for an ethical waiver by the designated ethics
officer in the Computer Science Department at University College London (UCL). 
The complete version of the surveys can be found in 
Appendix~\ref{appendixA}.

\subsubsection{The answerer survey} 
The survey contains 11 questions: 7 Likert's
scale questions, 3 yes/no questions, and one open-ended question for additional
comments. The first two questions are mandatory while the other 9 questions will
be shown to the participants based on their previous answers. The survey
collects information of the participant's software development experience, the
experience of answering Stack Overflow questions, sources of the Stack Overflow
snippets, awareness of outdated code in their answers, concerns regarding
license when they copy code snippets to Stack Overflow, and additional
feedbacks. The survey was open for participation for 50 days, from 25 July 2017
to 12 September 2017, before we collected and analysed the responses.

\subsubsection{The visitor survey} 
The survey consists of 16 questions: 9 Likert's
scale questions, 3 yes/no questions, 2 multiple-choice questions, and 2
open-ended questions. The first four questions are mandatory while the other 12
questions will be shown to the participants based on their previous answers. The
survey collects information of the participant's software development
experience, the importance of Stack Overflow, reasons for reusing Stack Overflow
snippets, problems from Stack Overflow snippets, licensing of code on Stack
Overflow, and additional feedbacks. The survey was open for participation for 50
days, from 25 July 2017 to 12 September 2017, before we collected and analysed
the responses.

\subsection{Participant Selection}

\subsubsection{The answerer survey} 
We selected the participants for our answerer survey based on their Stack
Overflow reputations. On Stack Overflow, a user's reputation reflects how much
the community trusts the user. A user earns reputation when he or she receives
up votes for good questions and useful answers. Accepted answers receive more
reputation score than questions and regular answers\footnote{Stack Overflow
	Reputation:~\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
Overflow reputation is an indicator of user's skills and their involvement in
asking and answering questions on the site.

@@

The participants were invited to take the survey via email addresses publicly
available on their Stack Overflow and GitHub profiles. We selected the answerers
based on their all-time reputation ranking\footnote{Stack Overflow Users (data as of
	25 July 2017):~\url{https://stackoverflow.com/users?tab=Reputation&filter=all}}
and separated them into two groups (see Table~\ref{tab:answerers}) so that we
can compare the results or observe similar patterns between them. The first
group had reputation from 963,731 (the highest) to 7,674, and the second group
had reputation from 7,636 to 6,999 which we sent out 300 and 307 emails
(excluding undelivered ones) respectively.

\subsubsection{The visitor survey} 
We adopted non-probability convenient sampling to invite participants for this
survey. Participation in the survey requires experience of
visiting Stack Overflow for solving programming tasks at least once. The
participants were invited to take the survey via five channels. The first
channel is via the first author's social media post (Facebook) where the he
invited friends who are software developers and have experience of copying code
snippets from Stack Overflow to take the survey. The second channel is a popular
technology news and media community in Thailand called \textsf{blognone.com} which
attracts a high number of Thai software developers. The first author posted an
invitation to the visitor survey in a discussion forum mentioning the
requirements to take the survey. The third channel collects answers from the
University of Molise from help of an external researcher. The last two
channels are from a \textsf{comp.lang.java.programmer} Google groups and Software
Engineering Facebook page. The number of participants taken the survey is shown in
Table~\ref{tab:visitors}.

\begin{table}
	\centering
	\caption{The Stack Overflow visitors taken the survey}
	\label{tab:visitors}
	\begin{tabular}{lr}
		\toprule
		Group & Answers \\
		\midrule
		Social media (Facebook posts) & 47 \\
		Blognone.com & 32 \\
		University of Molise & 6 \\
		comp.lang.java.programmer & 3 \\
		Software Engineering Facebook page & 1 \\
		\midrule
		Total & 89 \\
		\bottomrule
	\end{tabular}
\end{table}

\subsection{Data Analysis}
Google Forms provide a helpful summary of responses to the online surveys. We
relied on the summary from Google Forms when analysing the answers from the
answerer survey. For the visitor survey, since we created a copy of the survey for each
group of the participants, we downloaded the responses in comma-separated values
(CSV) files and merged the results before the analysis.

\section{Results and Discussions}
We collected and analysed the results after we closed the surveys on 12
September 2017. We now discuss the results separately for the answerer and the
visitor survey.

\subsection{The answerer survey}
We received 117 answers (39\% response rate) from the first group and 85 answers
(28\% response rate) from the second group of Stack Overflow answerers. The response
rate from both groups was high considered other online survey in software
engineering that received approximately 14--20\%~\FIXME{double-check the
	citation again for the magic numbers.}~\citep{Punter2003}.

\subsubsection{General Information}
%General information of the answerers' experience and frequency of answering 
%questions on Stack Overflow with code snippets as discussed below.

@@

\subsection{Internal Validity}
We targeted the participants for the answerer survey based on their Stack Overflow
reputation instead of random sampling. This is because reflects the developers
involvement in asking and answering questions on the site. Thus, our findings
capture awareness and experience of experienced Stack Overflow developers. Moreover,
due to a large number of users on Stack Overflow, we could invite only 607
highly-ranked developers to participate in the study.

We selected the participants for the visitor survey based on convenient sampling which
could suffer from bias and outliers.

\subsection{External Validity} 
While the reputation is a good proxy to reflect the amount of answers the
developers have given, it might not cover all kinds of answerers on Stack
Overflow. The answerers who have lower-reputation than 6,999 were not invited to
our study and their awareness and experience may differ from our findings.

At least 39\% of the participants in the visitor survey are from
\textsf{blognone.com} which is based in Thailand. Due to working culture,
answers from this group of developers may only represent software developers in
Thailand. We alleviate this concern by inviting participants from other groups,
e.g.~University of Molise in Italy, comp.lang.java.programmer, and Software
Engineering Facebook group.
